\setcounter{page}{5}
\addcontentsline{toc}{chapter}{Abstract}

     \begin{center}
{\large\textbf{Abstract}}
    \end{center}
\vspace*{0.4cm}

The three-dimensional picture of quarks and gluons in the nucleon is set to be 
revealed through deeply virtual Compton scattering (DVCS). With the absence of 
a free neutron target, the deuterium target represents the simplest nucleus to 
be used to probe the internal 3D partonic structure of the quasi-free neutron.  
We propose here to measure the beam spin asymmetry (BSA) in incoherent neutron DVCS 
together with the approved E-xxxxx experiment (BONUS12) within the run group F, 
using the same beam time, simply with addition of beam polarization. The DVCS BSA on the
quasi-free neutron will be measured in a wide range of kinematics by tagging 
the scattered electron and the real photon final state with the spectator 
proton. We will also measure BSA with all final state particles detected
including the struck 
neutron. The proposed measurements is highly complementary with the approved CLAS12 
experiment E12-11-003, which will also measure the quasi-free neutron DVCS by 
detecting the scattered neutron, but not the spectator proton. 
Indeed, besides providing more data for neutron DVCS, it would allow comparing 
the measurements of BSA of neutron DVCS, from the E12-11-003 and with
the two methods proposed herein. This comparison will help to understand the impact of 
nuclear effects, such as the final state interactions (FSI) and Fermi motion 
on the measurement of the neutron DVCS.

\newpage

